### 2020-05-25 writeup/proof_taskonomy.tex
transfer wip

\section{Extension to Transfer Learning}

We study the transfer function of taskonomy \cite{ZSSGM18}.
The algorithm is as follows.
First, we obtain the single-task estimator $\hat{\beta}_i$ from every task, for $1\le i \le k$.
This forms the shared representation $B$ in Algorithm \ref{alg_estimator}.
Then, we learn the output layer on the target task.
We use our tools to analyze this setting as follows.

>>>>

\section{Extension to the Transfer Function of Taskonomy}

We study the transfer function of taskonomy \cite{ZSSGM18}.
The algorithm is as follows.
First, we obtain the single-task estimator $\hat{\beta}_i$ from every task, for $1\le i \le k$.
This forms the shared representation $B$ in Algorithm \ref{alg_estimator}.
Then, we learn the output layer on the target task by solving equation \eqref{eq_mtl}.
We use our tools to compare the estimator of this setting to single-task learning.

### 2020-05-25 writeup/transfer.tex
restructure sec 3
edits
transfer wip

\section{Dissecting the Effects of Different Task Data in Multi-Task learning}\label{sec_insight}

@@

\subsection{Task Model Similarity}\label{sec_dist}

@@

\subsection{Data Size and Efficiency}\label{sec_data}

@@

\section{Extension to the Transfer Function of Taskonomy}

We study the transfer function of taskonomy \cite{ZSSGM18}.
The algorithm is as follows.
First, we obtain the single-task estimator $\hat{\beta}_i$ from every task, for $1\le i \le k$.
This forms the shared representation $B$ in Algorithm \ref{alg_estimator}.
Then, we learn the output layer on the target task.
We use our tools to analyze this setting as follows.

>>>>

\section{Positive versus Negative Transfer in Multi-Task learning}
\label{sec_insight}

@@

\subsection{Task Model Similarity}\label{sec_similarity}

@@

\subsection{Data Size and Efficiency}\label{sec_data_size}

@@
